Millions of Type Errors

### 2023-04-01 oopsla23/paper.tex
ideas for 3rd contribution
shorter title, 'non-invasive tel.'

\title{Millions of Type Errors}
\subtitle{Using Telemetry To Measure The User Experience Of Type Error Reporting}

@@

@@

TT =
no user ID, no machine ID,
no time-ordered traces,
public process to decide what to collect

@@

>>>>

\title{Millions of Type Errors}
\subtitle{Non-Invasive Telemetry to Measure User Experience}

@@

  \item
    \FILL{} any surprises when doing the analysis?
    Note, no ML for analysis, we do not have a corpus of text.

@@

@@

TT:
no user ID, no machine ID,
no time-ordered traces,
public process to decide what to collect

kindle track every tap (page turn etc),
enables whispersync feature,
drove design of navigation tools,
opt-out possible~\cite{kindle-telemetry}

vscode: usage data, crash reports, error data (not a crash but unexpected);
save file, open terminal, copy-paste, autocomplete offered, git queries, machine id,
session id, timestamp,
opt-out may be possible, but not for all usage data (per license, sec 2a) and
every extension can do its own thing~\cite{vscode-telemetry}

.NET SDK and .NET CLI:
crash reports, command invoked, args, hashed cwd, timings;
more listed online;
published in aggregate under CC-BY
opt-out possible~\cite{dotnet-telemetry}
